---
title: "Sales Report"
author: "Tommy Weber"
date: "06/19/2023"
output:
  pdf_document:
    toc: yes
    toc_depth: '2'
  html_document:
    code_folding: none
    df_print: paged
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE,
    eval = TRUE,
    message = FALSE,
    warning = FALSE,
    dpi = 300,
    fig.align = "center"
    )
```


```{r, echo=FALSE}
library(tidyverse)
library(lubridate)
library(plotly)

source("../content/01_journal/utility.R")

# Bike data
bikes_tbl      <- readRDS("../../bikes_tbl.rds")
bikeshops_tbl  <- readRDS("../../bikeshops_tbl.rds")
orderlines_tbl <- readRDS("../../orderlines_tbl.rds")

bike_orderlines_tbl <- orderlines_tbl %>%
    left_join(bikes_tbl,     by = c("product_id" = "bike_id")) %>%
    left_join(bikeshops_tbl, by = c("customer_id" = "bikeshop_id")) %>%
    mutate(total_price = price_euro * quantity)

```


\pagebreak
# Total Sales Charts {.tabset .tabset-fade .tabset-pills}

## Quarterly Sales Trends

```{r, echo=FALSE, out.height="500px", out.width="100%"}
plot_total_sales(unit = "quarter", date_format = "%B %d, %Y", interactive = FALSE)
```

\pagebreak
## Monthly Sales Trends

```{r, echo=FALSE, out.height="500px", out.width="100%"}
plot_total_sales(unit = "month", date_format = "%B %d, %Y", interactive = FALSE)
```

\pagebreak
## Weekly Sales Trends

```{r, echo=FALSE, out.height="500px", out.width="100%"}
plot_total_sales(unit = "week", date_format = "%B %d, %Y", interactive = FALSE)
```

\pagebreak
# Category Sales Charts {.tabset .tabset-fade .tabset-pills}

## Road {.tabset .tabset-fade}

### Quarterly Sales Trends

```{r, echo=FALSE, fig.height=7, out.width="100%"}
plot_categories(category_1 = "Road",
                category_2 = "All",
                unit = "quarter", 
                date_format = "%B %Y",
                ncol = 1, scales = "free_y",
                interactive = FALSE)
```

\pagebreak
### Monthly Sales Trends

```{r, echo=FALSE, fig.height=7, out.width="100%"}
plot_categories(category_1 = "Road",
                category_2 = "All",
                unit = "month", 
                date_format = "%B %Y",
                ncol = 1, scales = "free_y",
                interactive = FALSE)
```

\pagebreak
### Weekly Sales Trends

```{r, echo=FALSE, fig.height=7, out.width="100%"}
plot_categories(category_1 = "Road",
                category_2 = "All",
                unit = "week", 
                date_format = "%B %Y",
                ncol = 1, scales = "free_y",
                interactive = FALSE)
```

\pagebreak
## Mountain {.tabset .tabset-fade}

### Quarterly Sales Trends

```{r, echo=FALSE, fig.height=7, out.width="100%"}
plot_categories(category_1 = "Mountain",
                category_2 = "All",
                unit = "quarter", 
                date_format = "%B %Y",
                ncol = 1, scales = "free_y",
                interactive = FALSE)
```

\pagebreak
### Monthly Sales Trends

```{r, echo=FALSE, fig.height=7, out.width="100%"}
plot_categories(category_1 = "Mountain",
                category_2 = "All",
                unit = "month", 
                date_format = "%B %Y",
                ncol = 1, scales = "free_y",
                interactive = FALSE)
```

\pagebreak
### Weekly Sales Trends

```{r, echo=FALSE, fig.height=7, out.width="100%"}
plot_categories(category_1 = "Mountain",
                category_2 = "All",
                unit = "week", 
                date_format = "%B %Y",
                ncol = 1, scales = "free_y",
                interactive = FALSE)
```

